\documentclass[11pt, a4paper]{cv}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage{geometry}
\geometry{left=2.0cm, top=1.5cm, right=2.0cm, bottom=2.0cm, footskip=.5cm}
\pagenumbering{gobble}

\begin{document}



\cvsection{info}{Personal Information}

dassdadsdadsa

\cvsection{user}{About Me}

\aboutme
{

	\faQuoteLeft \space Master finalist in Electrical Engineering, with a wide technological background in Embedded Systems and Telecommunications. I am currently looking for new challenges in my professional field and I believe I can be a great addition to your team.

	I consider myself to be a highly motivated professional with good problem solving skills and objective-oriented. I face any task to me entrusted in a serious and rigorous way.

	I am passionate about programming and Linux in general. Solid programming skills in C, C\#, Java, and eager to further improve my skills in C++ , Javascript, SQL, and Python. 

	In my spare time, I like to learn other tools and programming languages. I'm currently diving into the containers / docker world. \faQuoteRight

}

\cvsection{graduation-cap}{Education}

dasdsadssdsda

\cvsection{code}{Skills}

\begin{multicols}{2}
	Programing Languages \newline
	Tools
\end{multicols}

\begin{multicols}{4}
	\noindent
	Java \newline
	C \newline
	C++ \newline
	C\# \newline
	Pyton \newline
	Javascript \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	Java \newline
	C \newline
	C++ \newline
	C\# \newline
	Pyton \newline
	Javascript \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle \newline
	\faCircle\faCircle\faCircle\faCircle\faCircle
\end{multicols}

\cvsection{list-ul}{Projects}

dadsdas

\end{document}